\begin{center}
{\huge \bf Acknowledgements}
\line(1,0){430}
\end{center}



I owe a huge debt of gratitude to God Almighty for His unconditional and resilient love cum compassion towards me. I appreciate him for the intellectual acumen He amply bestowed on me before, during and after this industrial training.\\ 

This project based internship was made possible by funding from my Guardians, benefactors and sponsors, Engr. \& Mrs. Sunday Idogun, my amiable sister, Mrs. Modupe Igbekoyi, and her husband, Mr. Idowu Igbekoyi, my great brother, Mr. Festus Idogun, and all my family members. You have all been awesome to me. I would like to thank my industry ­based supervisor, Oluboyo Charles Oluwaseun, for his encouragement, supports in all aspects, and timely help. I am favoured to have been under your tutelage. Special thanks are extended to Frances Nnamadim, a Business Analyst and \ac{UI}/\ac{UX} designer, who never seemed to be tired of imparting knowledge and writing comments and remarks, for discussions, feedback, ideas, and for help on the various projects done. I would also like to thank Amuche Benson­Onyeibor, who extended her generosity and was kind enough to offer comments and suggestions while implementing some projects. My grateful thanks go to all the people at \textit{ip}NX Nigeria Limited for the pleasant co­operation and hospitality they offered during my stay, particularly Shade Efiong­Bassey, the Human Resources Managers, and Administrators.\\

 
Finally, I want to thank Dr. Erastus Olarewaju Ogunti and Dr. (Mrs) Folasade Mojisola Dahunsi, Ag. Head Of Computer Engineering Department, Federal University of Technology, Akure, for their unpredented career advice and efforts to help secure internship placement.

\clearpage