%Abstract
\begin{center}
	{\huge \bf Abstract}
	\line(1,0){430}
\end{center}

This paper reports a six-month Internship with the Research and System Architecture department at \textit{ip}NX Nigeria Limited, Victoria Island, Lagos.\\ 

My tasks were to engineer, develop and deploy customer-centric software products while employing modern Software development paradigms and practices. Some projects require data visualization in which communication between Front-end and Back-end asynchronously \ac{JSON} over \ac{XHR} using \ac{AJAX} while others involve implementing complex algorithms such as the Materialized Path Algorithm to provide some required complex features as contained in the Software Requirement Specification document. Such implemented complex features include but not limited to a Threaded Commenting System, Full-text search system using PostgreSQL's full-text search engine, a live chat system and other basic \ac{CRUD} processes using Flask and Django frameworks as well as PostgreSQL and SQLite databases. Most of the software projects were wholly written in Python, an interpreted, high-level, general-purpose programming language created by Guido van Rossum and first released in 1991 that lets one work quickly and integrate systems more effectively. Few other projects such as a Web crawler and Recommender system were implemented in Julia, a new programming language offering a unique combination of performance and productivity that promises to change scientific computing, and programming in general.
Julia picks the best parts of existing programming languages, providing out-of-the-box features such as a powerful \ac{REPL}, an expressive syntax, Lisp-style metaprogramming capabilities, powerful numeric and scientific programming libraries, a built-in package manager, efficient Unicode support, and easily called C and Python functions.\\

System/Linux Administration works were also embarked upon ranging from deploying already developed applications to a Linux server using Apache2 and nginx to complying with versioning and back-end compatibility of resources. In cooperation with a notable senior staff in the department of Business Intelligence and Data Analytics (BIDA), I designed and developed from scratch a complex blogging web application  primarily to bring together tech enthusiasts.  Syntax highlighting was implemented using Primejs and Django-ckeditor was used as "\ac{WYSIWYG}" rich texts or documents editor.
\clearpage